Fixing Vulnerabilities Hinders Maintainability

### 2019-02-05 paper/ICPC19/icpc19.tex
discussion fixes

\textbf{\textit{Security refactorings harm the maintainability of open-source software.}}
%
We found that $40.2\%$ of the security refactoring have a negative impact on the
maintainability of open-source software (cf. Figure~\ref{fig:secvsreg}). This raises
a new tradeoff when developers need to fix vulnerabilities on their projects
because they might be affecting the software maintainability or even introducing
new vulnerabilities. This study exhibits evidence that developers may have to
reduce maintainability for the sake of security. We understand that developers
should be able to produce secure code without affecting the maintainability of
their projects. But there are still some concerns that need to be addressed:
\begin{itemize}
	\item \textbf{Documentation} of software must provide developers with the
	best practices to implement secure and maintainable software. Unmaintainable
	code is difficult to test, analyze and re-use.
	\item\textbf{Programming Languages} should provide new design patterns to easily
	implement security patterns without endangering maintainability. One example is
	the need for designing new authorization mechanisms since these are one of the most
	complex security features to implement.
	Some mechanisms might assist authorization maintenance in long run, such as
	the combination of \texttt{HTTP} filters with \texttt{Spring Security}
	annotations.

	\item \textbf{Software Developers} lack the knowledge to create secure and
	maintainable code. Mainly because academic curriculums are not yet prepared
	to educate these matters to them. Universities should do their part on making
	this possible. Online services such as BCH have also a great potential to help
	developers to be more aware of the maintainability issues introduced by their
	changes. Thus, developers can put more work into improving their code maintainability
	and avoid common issues such as code duplication.

>>>>

\textbf{\textit{Security refactorings harm the maintainability of open-source software.}}
%
We found that $40.2\%$ of the security refactoring have a negative impact on the
maintainability of open-source software (cf. Figure~\ref{fig:secvsreg}). This raises
a new tradeoff when developers need to fix vulnerabilities on their projects
because they might be affecting the software maintainability or even introducing
new vulnerabilities. This study exhibits evidence that developers may have to
reduce maintainability for the sake of security. We understand that developers
should be able to produce secure code without affecting the maintainability of
their projects. But there are still some concerns that need to be addressed:
\begin{itemize}
	\item \textbf{Documentation} of software must provide developers with the
	best practices to implement secure and maintainable software. Unmaintainable
	code is difficult to test, analyze and re-use.

	\item\textbf{Programming Languages} should provide new design patterns to
	easily implement security patterns without endangering maintainability.
	Ultimately, new programming languages, both secure and maintainable by design,
	may be designed to help developers be highly productive when writing and
	maintaing  secure applications. One example is the need for designing new
	authorization mechanisms since these are one of the most complex security
	features to implement.

	\item \textbf{Software Developers} lack the knowledge to create secure and
	maintainable code. Mainly because academic curricula are not yet prepared
	to properly educate them. Universities should do their part on making
	this possible. Online services such as BCH have also a great potential to help
	developers to be more aware of the maintainability issues introduced by their
	changes. Thus, developers can put more work into improving their code maintainability
	and avoid common issues such as code duplication.
